\section{Introduction}
\label{se:introduction}

In the second generation of intact stability criteria, the IMO has addressed the importance of ships having sufficient roll damping to avoid parametric roll and large roll motions in dead ship condition as well as excessive acceleration \parencite{imo_finalization_2016}.
Modern ship designs, especially volume carriers seem to be more vulnerable to these phenomena. So that these topics have gained more attention since the late 90’s where there were some accidents such as the APL China casualty.
\parencite{soder_ikeda_2019} showed that a relatively small difference in the roll damping prediction can be enough to make the difference between sever roll angles and hardly noticeable responses. Having a good description of roll damping is therefore crucial.
Since the scale effect of the damping is mainly associated with the skin friction on ship hulls and the friction only contributes very little to a full scale ship's total roll damping, experimental model tests is a widely accepted method to estimate a ship's roll damping \parencite{imo_1200_2006}. A lot of research activities have been put on methods to estimate roll damping from experimental model tests. For example, \parencite[]{hua_approximation_2011} investigated a second order oscillator model to approximate the a ship's roll damping based on both experiments at different scales and numerical calculations.
As the rapid increase of computation capability, the CFD methods have also been used to calculate the roll damping as in \parencite{kristiansen_experimental_2014} and \parencite{henry_peter_piehl_ship_2016}.  

However, in the early stage of ship design, when only limited information is available, such as the ship's principal dimensions and the basic hull geometry, computational fluid dynamics or experimental model tests are not feasible options.
Therefore, simpler methods are widely used. Simpler strip theory methods can give quite accurate prediction of a ship's pitch, heave, sway and yaw motions, but often overestimates the roll motions because of significant viscous effects on the roll damping \parencite{kawahara_simple_2011}. Therefore other methods are used to obtain the roll damping at early design stage. Several semi-empirical methods were proposed in the late 70th as described by  \parencite{himeno_prediction_1981}. The most recognize method was developed in a series of research articles \parencite{ikeda_roll_1978,ikeda_eddy_1978,ikeda_roll_1979,ikeda_components_1978,ikeda_velocity_1979}, often referred to as the Ikeda's method. This method divides the roll damping into five damping components, i.e., the friction component, the eddy component, the lift component, the wave component and the bilge keel component. This semi-empirical method is also recommended by \parencite{ittc_ittc_2011}. As reported by  \parencite{kawahara_simple_2011} and \parencite{soder_ikeda_2019}, Ikeda's method may not work well for unconventional ships, such as container ship and PCTC with pronounced flare bow and stern structures. 
There also exist a simplified version of  Ikeda's method \parencite{kawahara_simple_2011} (SI-method) which was created as a regression on   calculation results from Ikeda's method for a series of parameterized hull shapes. 

The main objective of this paper is to investigate the accuracy of the SI-method for modern ships using more than 250 roll decay tests conducted at SSPA during the past 15 years. The second objective is to investigate if the accuracy of the SI-method can be improved for modern ships or if a complete new method is needed. 

To make the completeness of the paper section \ref{se:methods_for_prediction_and_analysis} presents the basic governing equations of roll motions and how roll damping can be obtained from roll decay tests and the SI-method. 
The roll decay test database is presented in section \ref{se:accuracy_SI_method}, as well as the roll damping estimated by the system identification techniques as damping references, which are compared with the SI-method to identify weaknesses and strengths of this method. Section \ref{se:correction_SI_method} proposes a new regression-based method to improve the accuracy of roll damping in comparison with the SI-method. Conclusions are given in section \ref{se:conclusions}.  
