\section{Methods for prediction and analysis of roll damping}
\label{se:methods_for_prediction_and_analysis}
%\subsection{Equations}
%\label{se:equations}
From roll decay tests roll damping coefficients are normally derived based on the
logarithmic decrement of the roll peaks. However, this approach is sensitive to lowfrequency disturbances and noise, which does not have to be a problem in controlled
model test environment, but is difficult to avoid during full scale tests. An alternative
and more robust approach, which utilizes full time series of roll decay tests and
not only the peaks, is the numerical Parameter Identification Technique (PIT) as
described in IMO (2006) and also used in Bulian (2004). In this approach a numerical
solution to a one degree of freedom roll equation is fitted to the roll decay time series
by tuning the parameters in the roll equation.
To evaluate the performed tests, a modified version of the PIT approach is developed. This modified approach adds a time-dependent second-degree polynomial to
the fitting, that later can be separated from the solution to account for low frequency
disturbances. The roll equation that is used for the evaluation has a linear-quadratic
10 Assessment of Ship Roll Damping Through … 183
damping dependence and a linear restoring term. It should be noted that even though
the approach could well handle roll equations with higher order of non-linearities in
the damping term as well as a non-linear restoring term, the limited amplitudes at
which the roll decay tests was conducted cannot motivate advantages of higher order
models.
The equation of a freely oscillating roll motion with linear-quadratic damping can
in non-dimensional form be expressed as

The roll motion can be written as \cite{himeno_prediction_1981}:
\input{equations/roll_equation_himeno}

The equation express the roll moment [Nm] along a longitudinal axis though the centre of gravity.
Where $A_{44}$ is the virtual mass moment of inertia, $B_{44}$ is the roll damping moment and $C_{44}$ is the restoring moment. $M_{44}$ represents the external moment (usually moment from external waves).



\textbf{should one put the following descrption in the experimental description.}
The roll damping moment $B_{44}$ is the primary interest in this paper. The $B_{44}$ is determined using model scale roll decay tests. $B_{44}$ is determined using system identification, by finding the best fit to the following equation:
\input{equations/roll_decay_equation_general_himeno}
The external moment is zero during a roll decay test, since there are no external forces present.

The $B_{44}$ can be expressed as a series expansion:  
$ B_{44} = B_1\cdot\dot{\phi} + B_2\cdot\dot{\phi}\left|\dot{\phi}\right| + B_3\cdot\dot{\phi}^3 + ...$

Truncating this series at the cubic term gives a "cubic model":
\input{equations/roll_decay_equation_cubic}

Truncating this series at the quadratic term gives a "quadratic model":Truncating this series at the quadratic term gives a "quadratic model":
\input{equations/roll_decay_equation_himeno_quadratic}

Truncating this series at the linear term gives a "linear model":
\input{equations/roll_decay_equation_himeno_linear}

Peter Piehl \cite{henry_peter_piehl_ship_nodate} shows an analytical solution to the linear model in equation \ref{eq:roll_decay_equation_himeno_linear}, where the natural frequency of the motion is obtained by:
\input{equations/omega0_equation}

The roll damping and the natural frequency can be made non dimensional using the following expressions \cite{himeno_prediction_1981}: 
\input{equations/B44_hat_equation}
\input{equations/omega_hat_equation}

%\input{2_methods_for_prediction_and_analysis/analytical_solution}
\input{2_methods_for_prediction_and_analysis/experimental_estimation}
\input{2_methods_for_prediction_and_analysis/empirical_formula_analysis}

\input{2_methods_for_prediction_and_analysis/simplified_ikeda}